\hypertarget{ux5f15ux7528ux6587ux732e}{%
    \section{引用文献}\label{ux5f15ux7528ux6587ux732e}}
\hypertarget{refs}{}
    \leavevmode\hypertarget{ref-Kunisato2012}{}%
Kunisato,Yoshihiko, Okamoto,Y., Ueda,K., Onoda,K., Okada,G., Yoshimura,S....Samejima,Kusuo (2012). \emph{Effects of depression on reward-based decision making and variability of action in probabilistic learning}, Journal of behavior therapy and experimental psychiatry, 43(4), 1088--1094.


\hypertarget{refs}{}
    \leavevmode\hypertarget{ref-Machino2014}{}%
Machino,A., Kunisato,Y., Matsumoto,T., Yoshimura,S., Ueda,K., Yamawaki,Y....Yamawaki,S. (2014). \emph{Possible involvement of rumination in gray matter abnormalities in persistent symptoms of major depression: an exploratory magnetic resonance imaging voxel-based morphometry study}, Journal of affective disorders, 168, 229--235.


\hypertarget{refs}{}
    \leavevmode\hypertarget{ref-kunisato2019}{}%
国里 愛彦・片平健太郎・沖村宰・山下祐一 (2019). うつに対する計算論的アプローチ:―強化学習モデルの観点から― 心理学評論, \emph{62}(1), 88-103.


\hypertarget{refs}{}
    \leavevmode\hypertarget{ref-Lewin}{}%
Lewin,K. (1951). \emph{Field theory in social science: Selected theoretical papers} , New York : Harper \& Brothers ( レヴィン・K 猪俣 佐登留(訳) (1951). 社会科学における場の理論 誠信書房 )


\hypertarget{refs}{}
    \leavevmode\hypertarget{ref-ux5742ux91ceux96c4ux4e8c1994}{}%
坂野 雄二・福井知美・熊野宏昭・堀江はるみ・川原健資・山本晴義…末松弘行 (1994). 新しい気分調査票の開発とその信頼性・妥当性の検討 心身医学, \emph{34}(8), 629--636.


\hypertarget{refs}{}
    \leavevmode\hypertarget{ref-lerner2015handbook}{}%
Lerner,R.M., Liben,S.L. \& Mueller,U. (2015). \emph{Handbook of child psychology and developmental science, cognitive processes} , NA : John Wiley \& Sons


